Causes and effects in Dichotomous Comparative Judgments: an information-theoretical system with plausible mechanism

### 2024-07-26 index.qmd
section:background; process:write

<!-- 1. What are DAGs? and how are they represented? -->
<!-- Graph theory is a branch of mathematics focused on the study of graphs. Graphs are mathematical structures that model pairwise relations between objects [@Gross_et_al_2018]. They can represent physical relations, such as electrical circuits and roadways, and less tangible structures, such as ecosystems and sociological relations. Graphs have proven useful in various fields, spanning statistics, computer science, operations research, and the natural and social sciences. One application in statistics that incorporates concepts from graph theory is causal inference. Specifically, the structural approach to causal inference uses directed acyclic graphs (DAG) to provide a formal and graphical representation of the causal structure of a system [@Neal_2020]. -->

<!-- A graph is a collection of nodes connected by edges. In a directed graph, edges extend from a *parent* node to a *child* node, with arrows indicating the direction of the causal influence. Two nodes that are connected by edge are said to be *adjacent* [@Gross_et_al_2018]. In a directed acyclic graph (DAG), the direction of causal influences does not loop back on itself, ensuring that the graph contains no cycles [@Neal_2020; @McElreath_2020]. -->

>>>>

<!-- 1. What are DAGs? and how are they represented? -->
Graph theory is a branch of mathematics focused on the study of graphs. Graphs are mathematical structures that model pairwise relations between objects. They can represent physical relations, such as electrical circuits and roadways, and less tangible structures, such as ecosystems and sociological relations[@Gross_et_al_2018]. Graphs have proven useful in various fields, spanning statistics, computer science, operations research, and the natural and social sciences. One application in statistics that incorporates concepts from graph theory is causal inference. Specifically, the structural approach to causal inference uses directed acyclic graphs (DAG) to provide a formal and graphical representation of the causal structure of a system [@Neal_2020].

A graph is a collection of nodes connected by edges. In a directed graph, edges extend from a *parent* node to a *child* node, with arrows indicating the direction of the causal influence. Two nodes that are connected by edge are said to be *adjacent* [@Gross_et_al_2018]. In a directed acyclic graph (DAG), the direction of causal influences does not loop back on itself, ensuring that the graph contains no cycles [@Neal_2020; @McElreath_2020].
